Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/10-introduction.tex
Fix contrib wording
Fix refs in intro/contrib

The contributions of this article are the following. \joseph{FIXME recheck le plan à la fin}
% Contributions
\begin{enumerate*}[(i)]
    \item We review state of the art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:TODO}).
    \item We introduce modern NER approaches and study their requirements in terms of training data, as well as the effects of pre-training (\cref{sec:TODO}).
    \item We show that Transformed-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:TODO}).
\end{enumerate*}

>>>>

The contributions of this article are the following. \joseph{FIXME recheck le plan à la fin}
% Contributions
\begin{enumerate*}[(i)]
    \item We review state of the art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:ocr-xp}).
    \item We evaluate modern NER approaches: their requirements in terms of training data, and the effects of pre-training (\cref{sec:ner-xp1}).
    \item We show that Transformed-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:ner-xp2}).
\end{enumerate*}
